\newcommand{\co}{\textsuperscript{†}}

%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research}


%-------------------------------------------------------------------------------
% Interests
%-------------------------------------------------------------------------------
\cvsubsection{Interests}

\begin{cventries}

\cventryLONG
	{Financial reporting and disclosure; information in financial markets; organizational economics with applications to managerial accounting; auditing}  

\end{cventries}

\vspace{.3cm}

%-------------------------------------------------------------------------------
% JMP
%-------------------------------------------------------------------------------
\cvsubsection{Job Market Paper}

\paperentry
	{The Gatekeeping Expert's Dilemma}   % title
	{Shunsuke Matsuno}   % author(s)
	{2025}   % year
	{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=5583773}{[link]} \href{https://shunsukematsuno.github.io/papers/supplementary-material_Gatekeeping-Experts-Dilemma.pdf}{[supplementary material]}}  % paper link
	{}   % link journal
	{}   % Journal
	{
	\begin{cvitems}  % Presentations
		\item {Presented at: EAA Talent Workshop, Columbia University, Hawaii Accounting Research Conference (scheduled)} 
		% \hfill\makebox[0pt][r]{\scriptsize(\co  Presented by coauthor)}}			
		\item {Media mention: CLS Blue Sky Blog \href{https://clsbluesky.law.columbia.edu/2025/11/12/how-strategic-vagueness-helps-gatekeepers-offer-guidance-without-being-gamed/}{[link]}}
	\end{cvitems}
	}
	{% Abstract
	Gatekeepers do not directly control agents but instead hold only veto power. They also have expertise and influence agents through communication. Their expertise helps agents' decisions, while veto power disciplines those decisions. However, gatekeepers face a dilemma: transparent communication may let agents game standards. How can gatekeeping experts guide behavior without being gamed? Many economic settings feature this tradeoff, including bank stress tests, environmental regulations, and financial auditing. Using financial auditing as the primary example, I show that strategic vagueness is the key: by revealing just enough to prevent the manager from inflating the report, the auditor guides the manager while preserving her gatekeeping power. This theoretical lens provides a novel rationale for why auditors predominantly accept clients' financial reports. Comparative statics reveals that greater gatekeeper independence or expertise sometimes dampens communication. This paper shows how communication and veto power make gatekeepers effective.
	}

\vspace{.5cm}
%-------------------------------------------------------------------------------
% Working Papers
%-------------------------------------------------------------------------------
\cvsubsection{Working Papers}{(\co Presented by coauthor)}

\paperentry
	{Mandatory vs. Voluntary Disclosure in the Dynamic Market for Lemons}   % title
	{Cyrus Aghamolla and Shunsuke Matsuno}   % author(s)
	{2024}   % year
	{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4680389}{[link]}}  % paper link
	{}   % link journal
	{R\&R at Review of Financial Studies}   % Journal
	{
	\begin{cvitems}  % Presentations
		\item {Presented at: Hawaii Accounting Research Conference\co, Columbia University, AES Winter Retreat\co, AES Annual Conference, Burton Accounting Conference\co} 
		% \hfill\makebox[0pt][r]{\scriptsize(\co  Presented by coauthor)}}			
		\item {Media mention: Duke FinReg Blog \href{https://sites.duke.edu/thefinregblog/2024/10/29/mandatory-vs-voluntary-disclosure-in-the-dynamic-market-for-lemons/}{[link]}}
	\end{cvitems}
	}
	{}

\paperentry
	{Disclosure, Signaling, and First-Mover (Dis)advantage}   % title
	{Shunsuke Matsuno}   % author(s)
	{2024}
	{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4985567}{[link]}}  % paper link
	{}   % link journal
	{}   % Journal
	{
	\begin{cvitems}  % Presentations
		\item {Presented at: Hawaii Accounting Research Conference, Columbia University, Duke University Accounting Theory Summer School, Junior Accounting Theory Conference}
	\end{cvitems}
	}
	{}

\paperentry
	{Conformity and Leadership in Organizations}
	{Shunsuke Matsuno}
	{2025}
	{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=5291646}[link]}
	{}
	{}
	{
	\begin{cvitems} % Presentations
		\item {Presented at: Columbia Theory Conference, Hawaii Accounting Research Conference, Kobe University Kanematsu Seminar, Zurich Accounting Research Workshop, AES Annual Conference}
	\end{cvitems}
	}
	{}

\paperentry
	{Strategic Patenting Under Financial Reporting Mandates}
	{Li Azinovic-Yang, Yue Chen, Shunsuke Matsuno, Sunho Yoo}
	{2025}
	{}
	{}
	{}
	{
	\begin{cvitems} % Presentations
		\item {Presented at: Zurich Accounting Research Workshop\co, CUHK\co, EAA\co, Columbia University\co, Duke University\co}
	\end{cvitems}
	}
	{}

\vspace{.3cm}

%------------------------------------------------------------------------------
% SUBSECTION TITLE
%-------------------------------------------------------------------------------
% \cvsubsection{Work in Progress}

% \paperentry
% 	{PCAOB Inspections, Dynamic Enforcement, and Deterrent Effect: Evidence from Structural Estimation}
% 	{Lisa Liu \& Shunsuke Matsuno}
% 	{}
% 	{}
% 	{}
% 	{}
% 	{
% 	\begin{cvitems} % Description(s) of tasks/responsibilities
% 		\item {Presented at: 2024 PCAOB/TAR Registered Reports Conference\co}
% 	\end{cvitems}
% 	}
% 	{}

% %%%%% If you want to use bibtex
% \cvsubsection{Published}
% \begin{refsection}
% 	\nocite{Selimi2015Cloud}
% 	\nocite{Khan2014Incentive}	
	
% 	\printbibliography[
% 	heading=none
% 	]
% \end{refsection}
